Efficient Coalition Formation \\ for Web Services

### 2013-05-29 papers/coalition-journal-extension/coalition_journal.tex
Changes

As mentioned in section \ref{webservice-communities}, communities are robust service providers with well stablished market share and reputation. By maintaining their reputation and performance, they attract  end users which choose them as service providers to perform their tasks. The community master is characterizd by a request rate $(R_M)$ from users. Each web service comes with a given QoS ($QoS_{ws}$) from which the throughput $T_{ws}$ is excluded. This exclusion allows us to build our analysis on the particular value of $T_{ws}$. Throughput is the average rate of tasks a web service can perform per time unit. Thus, web services perform tasks with an average output quality of $QoS_{ws}$ and a throughput rate of $T_{ws}$.
The community master uses a weighted fair queuing scheduling technique to distribute task ammoung its members.

>>>>

As mentioned in section \ref{webservice-communities}, communities are robust service providers with well stablished market share and reputation. By maintaining their reputation and performance, they attract  end users which choose them as service providers to perform their tasks. The community master is characterizd by a request rate $(R_C)$ from users. Each web service comes with a given QoS ($QoS_{ws}$) from which the throughput $Tr_{ws}$ is excluded. This exclusion allows us to build our analysis on the particular value of $Tr_{ws}$. Throughput is the average rate of tasks a web service can perform per time unit. Thus, web services perform tasks with an average output quality of $QoS_{ws}$ and a throughput rate of $Tr_{ws}$.

The community master uses a slightly modified \emph{weighted fair queuing} method to distribute task among its members. The goal is to allocate incoming tasks to web services with a rate matching throughput value of $Tr_{ws}$. In \emph{weighted fair queuing} method \emph{all} the input flow is multiplexed along different paths, however in our case if the input rate $(R_C)$ of the community is more than summation of throughput values of web services, some of the input tasks will be queued and served with delay. Thus, the amount of tasks performed by community is $\sum_{ws \in C}{(Tr_{ws})}$ when $\sum_{ws}{Tr_{ws}} \leq R_{C}$. However, when the community has more web services having more total throughput value than community's request rate $(R_C)$ the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $R_C \times \frac{Tr_{ws}}{\sum_{ws}{Tr_{ws}}}$ for each web service ($ws$) and the total rate of tasks being performed is $R_C$, the community's receiving request rate. The best situation for communities would be to have around the same number
